Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-10-01 final_submission/manuscript.tex
Added contributions

\section{Individual Contributions}
	//TODO

>>>>

\section{Individual Contributions}
	Paul handled mostly what covered the Stochastic Model, while Chris and Ryan worked on their own deterministic models. Everyone did a lot of their work in the presence of everyone else, while still putting in a lot of time at home. When it came time to submit, everyone was ready to work. All in all, lots of work put in from all team member and we were all satisfied with each other's work.
